\documentclass{resume}

\usepackage[left=0.25in,top=0.2in,right=0.25in,bottom=0.2in]{geometry}
\usepackage{multicol}

\name{Hugo Klepsch}
\address{ 5663 Appleby line \\ Burlington, ON L7M0P3  }
\address{ 905~$\cdot$~749~$\cdot$~4627 \\ hugo.klepsch@gmail.com }

\setlength{\columnsep}{0.1cm}

\begin{document}

  \begin{rSection}{Education}
    \begin{rSubsection}{University of Guelph}
    	{September 2015 - April 2020}
    	{ B.Comp. Software Engineering (Co-op), Honours }{Guelph, ON}
    	\item { Minor in Marketing }
    	\item { Dr. Mary McLeish Scholarship recipient (Highest GPA in Software engineering major)} 
    	\item { 2018 Braithwaite Business Scholarship} 
    	\item { Deans list }
	\end{rSubsection}
  \end{rSection}

  \begin{rSection}{Experience}
    \begin{rSubsection}{Arctic Wolf Networks}
    	{May 2018 - August 2018, January 2019 - August 2019}
    	{Member of technical staff}{Waterloo, ON}
    \item Used Esper, Apache Flink and Hadoop as part of a complex event processing pipeline to find 
    patterns in unbounded series of events.
    \item Part of team that pioneered construction of time-series anomaly detection system.
    \item Wrote independent auto-scaling services as part of a data processing pipeline that processed 8 
    billion messages per day.
    \item Added metrics and stability alerts to services.
    \end{rSubsection}

    \begin{rSubsection}{Carnegie Technologies}
    	{May 2017 - December 2017}
    	{Native back-end developer}{Waterloo, ON}
    \item Developed native C++ GPS and ephemeris libraries for use in embedded devices.
    \item Participated in the design of, and implemented REST style microservices using Node.js and 
    RabbitMQ.
    \item Designed and implemented C++ and Node.js RabbitMQ messaging library with support for a variety 
    of usage patterns (Consumer, Requester).
    \item Designed and implemented C++ JSON manipulation and validation library with support for 
    proprietary extensions to JSON schema specification.
    \end{rSubsection}
  \end{rSection}

  \begin{rSection}{Open Source Contributions}
  	\vspace{-0.5em}
  	\begin{center}
  		\begin{minipage}[t]{0.33333\textwidth}
  			\raggedright
  			{\bf avast-tl/retdec} \\
  			{\em December 2017}\\
  			\begin{list}{$\cdot$}{\leftmargin=0.8em}
  				\itemsep -0.5em \vspace{-0.2em}
  				\item {\small Proposed and added Docker
support}
  			\end{list}
  		\end{minipage}%
	  	\begin{minipage}[t]{0.33333\textwidth}
	  		\raggedright
	  		{\bf netmail-open/wjelement}
\\
  			{\em November 2017} \\
  			\begin{list}{$\cdot$}{\leftmargin=0.8em}
  				\itemsep -0.0em \vspace{-0.2em}
  				\item {\small Found and fixed bug causing library
not to compile with glibc}
  				\item {\small Added date-time support to JSON
schema verification system}
  			\end{list}
	  	\end{minipage}%
	  	\begin{minipage}[t]{0.33333\textwidth}
	  		\raggedright
	  		{\bf DefinitelyTyped/DefinitelyTyped}
\\
  			{\em July 2017} \\
  			\begin{list}{$\cdot$}{\leftmargin=0.8em}
  				\itemsep -0.0em \vspace{-0.2em}
  				\item {\small Added typescript type definitions for various Node.js libraries}
  			\end{list}
	  	\end{minipage}
	  \end{center}
  \end{rSection}

  \begin{rSection}{Volunteer History}
  	\begin{rSubsection}{Alumni and programming mentor, former student member}
  		{September 2013 – Present}
  		{M. M. Robinson high school's robotics club, “Rambotics”}{Burlington, ON}
  		\item {Created various sub-systems for functional mechanisms}
  		\item {Used PIDF closed-loop control, computer vision, motion profiling, path following, etc. for autonomous control of robot}
  		\item {Used encoders, potentiometers, limit switches, line followers \& cameras as input data for control loops}
  		\item {Taught high-school students about control flow, program structure, git \& the above}
  	\end{rSubsection}
  \end{rSection}

  \begin{rSection}{Volunteer History}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
      Protocols \& APIs & XML, JSON, SOAP, REST \\
      Databases & MySQL, PostgreSQL, Microsoft SQL \\
      Tools & SVN, Vim, Emacs
    \end{tabular}
  \end{rSection}

\end{document}
